---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library("tidyverse")

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSLhQYB9rsz31Uq3vlbLCGC53ZfJcBCcB7cSDx-ixG7tyeFiJD0JwQeSzWkMD12ap_ouIOCJf2J7C3F/pub?gid=774751212&single=true&output=csv")

latest_data <- logged_data %>% rename(
  response_date = 1,
  step_count = 2,
  step_location = 3,
  time_spent_walking = 4,
  minutes_in_gym = 5,
  type_of_workout = 6
)

steps <- latest_data$step_count
```

```{css}
body {
  font-family: "Comic Sans MS", "Comic Sans", cursive;
  line-height: 1.6;
  margin: 40px;
  color: #222;
  background-color: #fafafa;
}

h1, h2, h3 {
  font-family: "Comic Sans MS", "Comic Sans", cursive;
  color: #2c3e50;
  font-weight: 600;
}

img {
  margin: 20px 0;
  max-width: 100%;
}
```

## daily movement and exercise tracking

this report analyses daily physical activity data collected from google forms

the dataset includes information about:
step counts taken outside the house
main location of movement
time spent walking
time spent in the gym
type of workout performed

the purpose of this analysis is to explore patterns in daily movement and exercise habits using summaries and bar charts

## summary statistics for step count

the following values summarise the daily step counts recorded in the dataset
```{r}
paste("The average number of steps taken per day is", round(mean(steps), 0), "steps")
paste("The least amount of steps ever taken in a day was", min(steps), "steps")
paste("The maximum number of steps ever taken in a day was", max(steps), "steps")
```
## visualising movement patterns

the following bar charts show how participants distributed their movement across different categories

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = step_location),
           fill = "#6a0dad") +
  labs(
    title = "Main Location of Movement",
    x = "Location",
    y = "Number of Responses"
  )

latest_data %>%
  ggplot() +
  geom_bar(aes(x = time_spent_walking),
           fill = "#B2C248") +
  labs(
    title = "Time Spent Walking Outside",
    x = "Time Category",
    y = "Number of Responses"
  )

latest_data %>%
  ggplot() +
  geom_bar(aes(x = minutes_in_gym),
           fill = "#ff7f50") +
  labs(
    title = "Time Spent in the Gym",
    x = "Gym Time Category",
    y = "Number of Responses"
  )
```
